---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# traveltimeR: Travel Time R SDK

<!-- badges: start -->
<!-- badges: end -->

traveltimeR is a R SDK for Travel Time API (https://traveltime.com/). Travel Time API helps users find locations by journey time rather than using ‘as the crow flies’ distance. Time-based searching gives users more opportunities for personalisation and delivers a more relevant search.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` {r install, eval = FALSE}
# install.packages("devtools")
devtools::install_github("traveltime-dev/traveltime-sdk-r")
```

## Authentication

In order to authenticate with Travel Time API, you will have to supply the Application Id and Api Key. 

```{r auth, eval = FALSE}
library(traveltimeR)

#store your credentials in an environment variable
Sys.setenv(TRAVELTIME_ID = "YOUR_API_ID")
Sys.setenv(TRAVELTIME_KEY = "YOUR_API_KEY")
```

## Usage

Get [Isochrones](https://traveltime.com/docs/api/reference/isochrones):

```{r example, eval=FALSE}

departure_search <-
  make_search(id = "public transport from Trafalgar Square",
              departure_time = strftime(as.POSIXlt(Sys.time(), "UTC"), "%Y-%m-%dT%H:%M:%SZ"),
              travel_time = 900,
              coords = list(lat = 51.507609, lng = -0.128315),
              transportation = list(type = "public_transport"),
              properties = list('is_only_walking'))

result <- time_map(departure_searches = departure_search)

```

Also available:

* `time_filter()` [Distance Matrix (Time Filter)](https://traveltime.com/docs/api/reference/distance-matrix)
* `routes()` [Routes](https://traveltime.com/docs/api/reference/routes)
* `time_filter_fast()` [Time Filter (Fast)](https://traveltime.com/docs/api/reference/time-filter-fast)
* `time_filter_postcode_districts()` [Time Filter (Postcode Districts)](https://traveltime.com/docs/api/reference/postcode-district-filter)
* `time_filter_postcode_sectors()` [Time Filter (Postcode Sectors)](https://traveltime.com/docs/api/reference/postcode-sector-filter)
* `time_filter_postcodes()` [Time Filter (Postcodes)](https://traveltime.com/docs/api/reference/postcode-search)
* `geocoding()` [Geocoding (Search)](https://traveltime.com/docs/api/reference/geocoding-search)
* `geocoding_reverse()` [Reverse Geocoding](https://traveltime.com/docs/api/reference/geocoding-reverse)
* `map_info()` [Map Info](https://traveltime.com/docs/api/reference/map-info)
* `supported_locations()` [Supported Locations](https://traveltime.com/docs/api/reference/supported-locations)

Check function documentation for more examples.


